\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-27 related.tex
added cite for Verdi and added some draft text
added a citation

>>>>

In Verdi~\cite{wilcox2015verdi}, a distributed system is written and verified in Coq, and then OCaml code is produced for execution. Verdi cannot find liveness bugs. \psharp is also more production-friendly (works on a mainstream language). \PDComment{say few more stuff}

D3S~\cite{liu2008d3s} \PDComment{should read the paper, they say they are debugging running systems}
